A portable, annotation-based, visual stepper for Common Lisp

### 2020-02-25 paper/paper.tex
Small adjustments to the paper's text

\subsection{Source tracking code reader}\label{st-reader}

At its simplest definition, a source-tracking reader is a variation of
the Common Lisp \texttt{CL:READ} function that invokes a hook every
time a sub-form is read, and proceeds to pass to this hook a measure
of the character distance traveled so far to read it.  This enables
problems that need both the usual results of \texttt{CL:READ} and a
table of form-to-source-code pairings.

@@

\begin{enumerate}
\item \texttt{Eclector}\cite{eclector}, a self-described ``portable
  Common Lisp reader that is highly customizable and can return
  concrete syntax trees'', is a full realization of a Common Lisp code
  reader that doesn't rely on the implementation's.  Its
  distinguishing characteristic is the fact that ``concrete syntax
  trees'' are not \texttt{CONS} cells, rather CLOS objects that mimic
  the properties of such cells while also keeping ``concrete''
  source-file information;

@@

Its current limitations notwithstanding, the SLY/Emacs stepper
described in this essay is the nearest thing an effective, portable
and visual stepping facility available in the Common Lisp ecosystem.
In the process we have also described (1) a relatively simple (and
near-portable) technique for constructing a source-tracking reader in
terms of a compliant reader implementation and (2) a reliable
technique to carry over source-tracking information to macroexpansion.
It is conceivable that other debugging tools could be constructed from
either of these elements.

>>>>

\subsection{Source-tracking form reader}\label{st-reader}

At its simplest definition, a source-tracking form reader is a
variation of the Common Lisp \texttt{CL:READ} function that invokes a
hook every time a sub-form is read, and proceeds to pass to this hook
a measure of the character distance traveled so far to read it.  This
enables problems that need both the usual results of \texttt{CL:READ}
and a table of form-to-source-code pairings.

@@

\begin{enumerate}
\item \texttt{Eclector}\cite{eclector}, a self-described ``portable
  Common Lisp reader that is highly customizable and can return
  concrete syntax trees'', is a full realization of a Common Lisp code
  reader that doesn't rely on the implementation's.  Its
  distinguishing characteristic is the fact that ``concrete syntax
  trees'' are not \texttt{CONS} cells, rather CLOS objects that mimic
  the properties of such cells while also keeping ``concrete''
  source file information;

@@

Its current limitations notwithstanding, the SLY/Emacs stepper
described in this essay is the most effective example of a portable,
visual stepping facility for the Common Lisp ecosystem.  In
formulating its development we have also described (1) a simple,
portable technique for constructing a source-tracking reader in terms
of a compliant reader implementation and (2) a reliable technique to
carry over source-tracking information to macroexpansion.  It is
conceivable that other debugging tools could be constructed from
either of these elements.
